A Sample {\ttlit Proceedings of the VLDB Endowment} Paper in LaTeX Format\titlenote{for use with vldb.cls}

### 2018-03-13 paper/drlim.tex
removed an extra period
finished changes for todays meeting

The problem of dimensionality reduction, mapping a high dimensional group of entities onto a low dimensional manifold, is an important problem in many areas of machine learning. Dimensionality Reduction by Learning an Invariant Mapping is a technique for solving this problem by mapping points onto the manifold using a set of previously known matches and non-matches described by \cite{Hasdell:Siamese}. The goal of this technique is to minimize the distance between matched pairs and maximize the distance between unmatched pairs. This is accomplished using a network architecture know as a \textit{siamese} network. In this architecture there are two deep neural networks that share weights attached to a final layer that determines the distance between the output of the two hidden networks and minimizes the loss function. . To train the network a set of matched and non-matched pairs of inputs is sent through the network and the weights are adjusted to maximize or minimize distance accordingly.

>>>>

The problem of dimensionality reduction, mapping a high dimensional group of entities onto a low dimensional manifold, is an important problem in many areas of machine learning. Dimensionality Reduction by Learning an Invariant Mapping is a technique for solving this problem by mapping points onto the manifold using a set of previously known matches and non-matches described by \cite{Hasdell:Siamese}. We used this technique not for reducing the dimensionality, but for logically mapping points onto a vector space. The goal of this technique is to minimize the distance between matched pairs and maximize the distance between unmatched pairs. This is accomplished using a network architecture know as a \textit{siamese} network. In this architecture there are two deep neural networks that share weights attached to a final layer that determines the distance between the output of the two hidden networks and minimizes the loss function. To train the network a set of matched and non-matched pairs of inputs is sent through the network and the weights are adjusted to maximize or minimize distance accordingly. This is accomplished using the following loss function \[ L(W, Y, \vec{X}_1, \vec{X}_2) = (1 - Y)\frac{1}{2}(D_W)^2 + (Y)\frac{1}{2}\{max(0, m - (D_W))\}^2\] Where \(D_W\) is the euclidean distance between the two outputs, \textit{m} is a radius beyond which we ignore dissimilar points, and Y is the similar or dissimilar label.
